Residence time, a master variable of ecology, physiology, and natural selection

### 2015-09-08 analyses/2015_08_29_0720_ResTime.Rmd
modified main model, generated new png's and simulations data -KL

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/NandS_vs_ResTime.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/NandS_vs_ResTime_ByMotion.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/NandS_vs_ResTime_2ByMaxGrowthRate.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

p1 <- ggplot(sim.data, aes(x=h.tau, y=sim.data$total.abundance, group=sim.data$sim, 
                           colour=sim.data$max.growth.rate)) +
  scale_color_gradient(high="cyan") +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="Individuals") +
  labs(title="Total abundance") +
  guides(colour=FALSE) + 
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = .50)

p2 <- ggplot(sim.data, aes(x=h.tau, y=sim.data$species.richness, group=sim.data$sim, 
                           colour=sim.data$max.growth.rate)) +
  scale_color_gradient(high="cyan") +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="Number of species") +
  labs(title="Species richness") +
  guides(colour=FALSE) +
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = 1.0)

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/NandS_vs_ResTime_ByMaxActiveDisp.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

p1 <- ggplot(sim.data, aes(x=h.tau, y=sim.data$total.abundance, 
  group=sim.data$sim, colour=sim.data$max.active.dispersal)) +
  scale_color_gradient(high="darkseagreen") +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="Individuals") +
  labs(title="Total abundance") +
  guides(colour=FALSE) + 
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = .50)

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/EandB_vs_ResTime.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

p1 <- ggplot(sim.data, aes(x=h.tau, y=e.var, group=sim, colour=sim)) +
  scale_color_gradient(high="cyan") +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="Evar") +
  labs(title="Evenness") +
  guides(colour=FALSE) + 
  scale_x_log10() + 
  coord_fixed(ratio = 1.8)

p2 <- ggplot(sim.data, aes(x=h.tau, y=Whittaker.turnover, group=sim, colour=sim)) +
  scale_color_gradient(high="chartreuse") +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="Whittaker's") +
  labs(title="Species turnover") +
  guides(colour=FALSE) +
  scale_x_log10() +
  coord_fixed(ratio = 2.0)

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
plot.new()
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/Growth_and_Maint.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
plot.new()
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/Diversity_vs_N.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

par(mfrow=c(2, 2))

plot(N, Skew, xlab="Total abundance", log="xy",
     ylab="Skewness",
     main = "Rarity vs. N",
     col='plum')

plot(N, Nmax, xlab="Total abundance", log="xy",
     ylab="Nmax", 
     main = "Nmax vs. N",
     col='darkorange')

plot(N, e.var, xlab="Total abundance", log="xy",
     ylab="Species Evenness", 
     main = "Evenness vs. N",
     col='lightseagreen')

plot(N, S, xlab="Total abundance", log="xy",
     ylab="Species Richness", 
     main = "S vs. N",
     col='indianred')

dev.off()
```

>>>>

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/NandS_vs_ResTime.png',
      width = 1500, height = 1200, res=200, bg = "black")

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/NandS_vs_ResTime_ByMotion.png',
    width = 1500, height = 1200, res=200, bg = "black")

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
colors <- list('springgreen', 'greenyellow', 'yellow', 'cyan', 'magenta', 'deeppink', 'firebrick1',
               'aquamarine', 'hotpink', 'gold1', 'ghostwhite', 'darkseagreen1', 'red1', 'plum1',
               'olivedrab1', 'maroon1', 'floralwhite', 'lightsteelblue1', 'darkgoldenrod1')

good.names <- list('res.inflow','N.types','P.types','C.types','max.res.val','max.growth.rate',
              'max.met.maint','max.active.dispersal','logseries.a', 'flow.rate',
              'amplitude','frequency','phase','disturbance')

for(i in 1:ncol(sim.data)){
  name <- colnames(sim.data[i])

  if (name %in% good.names){
    print(name)
    color <- sample(colors, 1)

    name <- paste0('~/GitHub/hydrobide/results/figs/29_Aug/NandS_vs_ResTime_',name,'.png')
    png(filename = name, width = 1500, height = 1200, res=200, bg = "black")

    p1 <- ggplot(sim.data, aes(x=h.tau, y=sim.data$total.abundance, group=sim.data$sim, 
                           colour=sim.data[,i+1])) +
    scale_color_gradient(high=color) +
    geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
    theme_black() +
    labs(x= expression(tau), y="Individuals") +
    labs(title="Total abundance") +
    guides(colour=FALSE) + 
    scale_x_log10() +
    scale_y_log10() +
    coord_fixed(ratio = .50)

    p2 <- ggplot(sim.data, aes(x=h.tau, y=sim.data$species.richness, group=sim.data$sim, 
                           colour=sim.data[,i])) +
    scale_color_gradient(high=color) +
    geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
    theme_black() +
    geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
    theme_black() +
    labs(x= expression(tau), y="Number of species") +
    labs(title="Species richness") +
    guides(colour=FALSE) +
    scale_x_log10() +
    scale_y_log10() +
    coord_fixed(ratio = 1.0)

    multiplot(p1, p2, cols=2)
    dev.off()
    }
  }
```

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/EvennessAndTurnover_vs_ResTime.png',
      width = 1500, height = 1200, res=200, bg = "black")

p1 <- ggplot(sim.data, aes(x=h.tau, y=sim.data$e.var, 
                           group=sim.data$sim, colour=sim.data$sim)) +
  scale_color_gradient(high="cyan") +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="evenness") +
  labs(title="Species evenness") +
  guides(colour=FALSE) + 
  scale_x_log10() +
  coord_fixed(ratio = 2.5)

p2 <- ggplot(sim.data, aes(x=h.tau, y=sim.data$species.turnover, 
                           group=sim.data$sim, colour=sim.data$sim)) +
  scale_color_gradient(high="chartreuse") +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="turnover") +
  labs(title="Species turnover") +
  guides(colour=FALSE) +
  scale_x_log10() +
  coord_fixed(ratio = 2.5)

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
source("~/GitHub/hydrobide/tools/Rbin/multiplot.R")

png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/EvennessAndTurnover_vs_ResTime_ByMotion.png',
      width = 1500, height = 1200, res=200, bg = "black")

p1 <- ggplot(sim.data, aes(x=h.tau, y=sim.data$e.var, 
                           group=sim.data$sim, colour=sim.data$motion)) +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="evenness") +
  labs(title="Species evenness") +
  guides(colour=FALSE) + 
  scale_x_log10() +
  coord_fixed(ratio = 2.5)

p2 <- ggplot(sim.data, aes(x=h.tau, y=sim.data$species.turnover, 
                           group=sim.data$sim, colour=sim.data$motion)) +
  geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
  theme_black() +
  labs(x= expression(tau), y="turnover") +
  labs(title="Species turnover") +
  guides(colour=FALSE) +
  scale_x_log10() +
  coord_fixed(ratio = 2.5)

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
colors <- list('springgreen', 'greenyellow', 'yellow', 'cyan', 'magenta', 'deeppink', 'firebrick1',
               'aquamarine', 'hotpink', 'gold1', 'ghostwhite', 'darkseagreen1', 'blue1', 'plum1',
               'olivedrab1', 'maroon1', 'floralwhite', 'lightsteelblue1', 'darkgoldenrod1')

good.names <- list('res.inflow','N.types','P.types','C.types','max.res.val','max.growth.rate',
              'max.met.maint','max.active.dispersal','logseries.a', 'flow.rate',
              'amplitude','frequency','phase','disturbance')

for(i in 1:ncol(sim.data)){
  name <- colnames(sim.data[i])

  if (name %in% good.names){
    print(name)
    color <- sample(colors, 1)
    name <- paste0('~/GitHub/hydrobide/results/figs/29_Aug/EvennessAndTurnover_vs_ResTime_',name,'.png')
    png(filename = name, width = 1500, height = 1200, res=200, bg = "black")

    p1 <- ggplot(sim.data, aes(x=h.tau, y=sim.data$e.var, 
                               group=sim.data$sim, colour=sim.data[,i])) +
    scale_color_gradient(high = color) +
    geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
    theme_black() +
    labs(x= expression(tau), y="Evar") +
    labs(title="Evenness") +
    guides(colour=FALSE) + 
    scale_x_log10() + 
    coord_fixed(ratio = 2.5)

    p2 <- ggplot(sim.data, aes(x=h.tau, y=sim.data$species.turnover, 
                               group=sim.data$sim, colour=sim.data[,i])) +
    scale_color_gradient(high=color) +
    geom_smooth(mapping=NULL, data=NULL, se=F, stat="smooth") +
    theme_black() +
    labs(x= expression(tau), y="Whittaker's") +
    labs(title="Species turnover") +
    guides(colour=FALSE) +
    scale_x_log10() +
    coord_fixed(ratio = 2.5)

    multiplot(p1, p2, cols=2)
    dev.off()
    }
  }
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=4}
plot.new()
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/Growth_and_Maint.png',
      width = 1500, height = 1200, res=200, bg = "black")

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
source("~/GitHub/hydrobide/tools/Rbin/multiplot.R")

lm_eqn <- function(df){
    m <- lm(log(y) ~ log(x), df)
    a = format(coef(m)[1], digits = 2) 
    b = format(coef(m)[2], digits = 2) 
    r2 = format(summary(m)$r.squared, digits = 3)
    bquote('S = ' ~ .(a) ~ N^{.(b)})
    }

png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/Diversity_vs_N.png',
      width = 1500, height = 1200, res=200, bg = "black")

df <- data.frame(x=sim.data$total.abundance, y=sim.data$species.richness)
p1 <- ggplot(sim.data, aes(x=sim.data$total.abundance, y=sim.data$species.richness)) +
  labs(title=lm_eqn(df)) +
  geom_point(colour="snow3") +
  geom_smooth(method='lm',colour="lawngreen", size=2) +
  theme_black() +
  labs(x= "Total abundance", y="Species richness") +
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = 1.6)

df <- data.frame(x=sim.data$total.abundance, y=sim.data$e.var)
p2 <- ggplot(sim.data, aes(x=sim.data$total.abundance, y=sim.data$e.var)) +
  labs(title=lm_eqn(df)) +
  geom_point(colour="snow3") +
  geom_smooth(method='lm', colour="lawngreen", size=2) +
  theme_black() +
  labs(x= "Total abundance", y="Species evenness") +
  scale_x_log10() +
  scale_y_log10() +
  ylim(0.01,1) +
  coord_fixed(ratio = 4.3)

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
source("~/GitHub/hydrobide/tools/Rbin/multiplot.R")

lm_eqn <- function(df){
    m <- lm(log(y) ~ log(x), df, na.action=na.exclude)
    a = format(coef(m)[1], digits = 2) 
    b = format(coef(m)[2], digits = 2) 
    r2 = format(summary(m)$r.squared, digits = 3)
    bquote('S = ' ~ .(a) ~ N^{.(b)} ~.(r2))
    }

png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/Diversity_vs_N2.png',
      width = 1500, height = 1200, res=200, bg = "black")

df <- data.frame(x=sim.data$total.abundance, y=sim.data$N.max)
p1 <- ggplot(sim.data, aes(x=sim.data$total.abundance, y=sim.data$N.max)) +
  labs(title=lm_eqn(df)) +
  geom_point(colour="snow3") +
  geom_smooth(method='lm',colour="lawngreen", size=2) +
  theme_black() +
  labs(x= "Total abundance", y="Nmax") +
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = 1)

multiplot(p1, cols=1)
dev.off()
```

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
source("~/GitHub/hydrobide/tools/Rbin/multiplot.R")

png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/Diversity_vs_N_ByMotion.png',
      width = 1500, height = 1200, res=200, bg = "black")

p1 <- ggplot(sim.data, aes(x=sim.data$total.abundance, y=sim.data$species.richness,
             group=sim.data$sim, colour=sim.data$motion)) +
  geom_point() +
  theme_black() +
  labs(x= "Total abundance", y="Species richness") +
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = 1.55)

p2 <- ggplot(sim.data, aes(x=sim.data$total.abundance, y=sim.data$e.var,
                           group=sim.data$sim, colour=sim.data$motion)) +
  geom_point() +
  theme_black() +
  labs(x= "Total abundance", y="Species evenness") +
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = 3.8)

p3 <- ggplot(sim.data, aes(x=sim.data$total.abundance, y=sim.data$N.max,
                           group=sim.data$sim, colour=sim.data$motion)) +
  geom_point() +
  theme_black() +
  labs(x= "Total abundance", y="Dominance") +
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = 1)

p4 <- ggplot(sim.data, aes(x=sim.data$total.abundance, y=sim.data$skew,
                           group=sim.data$sim, colour=sim.data$motion)) +
  geom_point() +
  theme_black() +
  labs(x= "Total abundance", y="Rarity") +
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = 1.4)

multiplot(p1, p2, p3, p4, cols=2)
dev.off()
```
